Introduction to\\ Swedish Civil Contingencies Agency (MSB) methodological support for introducing \ac{isms}.

### 2019-03-18 msbframework/msbintro/msbintro.tex
Added GAP analysis

\begin{frame}{Tieto incident}
  \begin{itemize}
    \item In 2011 Tieto got a hardware problem in one of their datacenters. This
      created disruptions in many of the companies customers IT-system. For
      example: 
      \begin{itemize}
        \item All the pharmacies got problems handing out prescription medicin for a
          time.
        \item The swedish vehivle inspection agency could not report the results
          from the vehicle inspections they did during this time.
        \item A large logistical company could not handle its operation
        \item Social offices in Nacka and Sollentuna were unable to pay child
          support
      \end{itemize}
  \end{itemize}
\end{frame}
\begin{frame}{1177 incident}
  \begin{itemize}
    \item In 2019 a sub-contractor of a sub-contractor for a company that was
      handling the IT-system for three swedish region health care call line,
      forgot to secure a backup server that stored the recordings from the phone
      calls.
    \item Resulted in around 2.7 million (around 170 000 hours) of recordings of
      confidential phone calls got accessible for the public.
    \item The recordings contains everything from medical symptoms to social
      security numbers.
  \end{itemize}
\end{frame}
\begin{frame}{The Swedish Transport Agency}
  \begin{itemize}
    \item In 2017 it was revealed that sensitive information from the Swedish
      Transport Agency database were made available for non-security screened
      employees abroad. 
    \item Information included:
      \begin{itemize}
        \item Driver licences (including picture)
        \item Company secrets
        \item Sensitive information about infrastructure (bridges, subways etc)
        \item Information that can be used to identify armoured cars.
      \end{itemize}
  \end{itemize}
\end{frame}
\begin{frame}{Swedish Public Employment Service}
  \begin{itemize}
    \item In 2019 it was found that the Swedish Publich Employment Services
      (arbetsförmedlingen) automatic system for reporting activity reports to
      the Swedish Social Insurance Agency (Försäkringskassan) sent incorrect
      reports.
    \item It was estimated that 10-15 percent of the decisions were incorrect.
    \item Resulted in that approximately 70 000 decisions could have been wrong.
  \end{itemize}
\end{frame}

@@

>>>>

\begin{frame}{Tieto incident}
  \begin{itemize}
    \item In 2011 Tieto got a hardware problem in one of their datacenters. This
      created disruptions in many of the companies customers IT-system. For
      example: 
      \begin{itemize}
        \item All the pharmacies got problems handing out prescription medicin for a
          time.
        \item The swedish vehivle inspection agency could not report the results
          from the vehicle inspections they did during this time.
        \item A large logistical company could not handle its operation
        \item Social offices in Nacka and Sollentuna were unable to pay child
          support
      \end{itemize}
  \end{itemize}
\end{frame}
\begin{frame}{1177 incident}
  \begin{itemize}
    \item In 2019 a sub-contractor of a sub-contractor for a company that was
      handling the IT-system for three swedish regions health care guides (1177)
      call line, forgot to secure a backup server that stored the recordings
      from the phone calls.
    \item Resulted in around 2.7 million (around 170 000 hours) of recordings of
      confidential phone calls got accessible for the public.
    \item The recordings contains everything from medical symptoms to social
      security numbers.
  \end{itemize}
\end{frame}
\begin{frame}{The Swedish Transport Agency}
  \begin{itemize}
    \item In 2017 it was revealed that sensitive information from the Swedish
      Transport Agency database were made available for non-security screened
      employees abroad. 
    \item Information included:
      \begin{itemize}
        \item Driver licences (including picture)
        \item Company secrets
        \item Sensitive information about infrastructure (bridges, subways etc)
        \item Information that can be used to identify armoured cars.
      \end{itemize}
  \end{itemize}
\end{frame}
\begin{frame}{Swedish Public Employment Service}
  \begin{itemize}
    \item In 2019 it was found that the Swedish Publich Employment Services
      (arbetsförmedlingen) automatic system for reporting activity reports to
      the Swedish Social Insurance Agency (Försäkringskassan) sent incorrect
      reports.
    \item It was estimated that 10-15 percent of the decisions were incorrect.
    \item Resulted in that approximately 70 000 decisions could have been wrong.
  \end{itemize}
\end{frame}

@@

\begin{frame}{GAP Analysis --- Statement of Applicability}
  Statement of Applicability (Uttalande om tillämplighet)
  \begin{itemize}
    \item What should be covered in the GAP-analysis?
    \item Select security meassures, either from previous analyses, or pick all.  
    \item Once finished, the organisation have a complete list of security
      meassures that are applicable to the organisation.
  \end{itemize}
\end{frame}
\begin{frame}{GAP Analysis --- Perform the GAP analysis}
  Based on the list of applicable security meassures
  \begin{itemize}
    \item Is the security meassure already in place?
    \item Estimate the severity of the security meassure.
    \item Describe the current status of this security meassurement.
  \end{itemize}
